\chapter{Introduction}\label{chap1}

\section{Overview}


Biometrics refers to metrics related to human characteristics. Biometric authentication authentication is used in computer science as a part of identification and access control\cite{biometrics}. \newline


There being mainly two sub discipline namely behavioral and physiological. Behavioral characteristics deals with gait, voice, rhythm and the latter deals with body size and shape like fingerprint, iris, DNA, etc\cite{biometrics}.\newline

In this project work we focus on gait analysis. Human gait can be analyzed different way, the common being image processing and accelerometer based, this latter being used for this project..\\



\section{Motivation of the Research Work}\label{sec1.1}



Biometric analysis can be of great use in medical field. There has been news of doctors using Fitbit to monitor patients heart beat in hospitals. It could be of great value to people who needs to keep track of their heart beat. \newline

Although there are many gadget similar to that, but they are costly and common people doesn’t considers investing in it. But almost every people have smartphone and even the basic ones these days have built in accelerometer. Here we use android app which logs accelerometer readings and process it to understand gait cycle and compare it with other leg.\newline

Variation arise in gait pattern of both legs when a person is ill or tired/not feeling well. This app can inform the subject if he/she needs to consult a doctor and more importantly being cost effective.
\newpage
\section{Organisation of the Report}\label{sec1.3}
\begin{itemize}
\item Data acquisition and storage
\item Noise removal and smoothing 
\item Feature template extraction and arriving at conclusion
\end{itemize}




